\documentclass[9pt]{exam} 
\addpoints
\pointsinmargin
\renewcommand{\partshook}{
%\setlength{\topsep}{2mm}
\setlength{\itemsep}{2mm}
}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb} %standard classy maths symbols
\usepackage[a4paper, margin=1in]{geometry} %makes it easy to specify where to put stuff on the page

\usepackage{tcolorbox} % basic but good package for boxes around text
\tcbset{colback=black!5!white}

\usepackage{tikz} % interval diagrams, sets, etc.

\begin{document}

\vspace{-4mm}

\textbf{Name:} \dotfill \hspace{3cm} (answers to the nearest percent)

\begin{questions} 
\question[3] From the axioms prove that $P(A) + P(\overline{A}) = 1$ for any event $A$.
\fillwithdottedlines{23mm}

\question[2] What is the chance of throwing at least one six with four fair dice?
\fillwithdottedlines{14mm}

\question We play a game of heads and tails \textbf{but the coin is not fair.} You win if the coin lands on tails in any of the first three throws (and we stop playing immediately), otherwise I win. Let $0 < p = P(H) < 1$.
\begin{parts}
\part[3] Represent the situation with a tree diagram.
\vfill

\part[1] What is the probability you win on the first toss? \dotfill
\part[1] What is the probability you win on the second toss? \dotfill
\part[1] What is the probability you win on the third toss? \dotfill
\part[1] What is the chance I win? \dotfill
\fillwithdottedlines{8mm}
\part[1] If $p=\frac{1}{2} \sqrt[3]{4}$, show that we have an equal chance to win. \dotfill
\fillwithdottedlines{8mm}
\end{parts}

\question[4] Unbelievably, 5\% of Dr. Jane's class forgot to do their homework. We know that
\begin{itemize}
\item 80\% of students who forgot their homework look nervous.
\item 10\% of students who did their homework look nervous anyway. 
\end{itemize}
When I see a student who looks nervous what is the probability that they forgot their homework?

\vspace{2mm}
\emph{Work on the back, and then write your answer (to the nearest percent) here.} \dotfill

\end{questions}


\begin{tcolorbox}

\textbf{Name of marker:} 

\begin{center}
\gradetable[h][questions]
\end{center}

\end{tcolorbox}

\end{document}